---
title: "The language of gratitude"
author: "Stefan Hartmann, Nils Hansson & Adrian Loerbroks"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    theme: flatly
    highlight: tango
    toc: true
    toc_float: true
    collapsed: false
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```



```{r, message = FALSE}

library(tidyverse)
library(ggbeeswarm)
library(patchwork)
library(readxl)
library(patchwork)
library(stringr)
library(stringi)
library(tidytext)
library(ngram)
library(quanteda)
library(vroom)
library(pbapply)
library(cluster)
library(wordcloud)
library(wordcloud2)
library(data.table)
library(DT)
library(collostructions) # available at sfla.ch

```

read data (tagged with [Spacy](https://spacy.io))
Tagged datasets [here](https://uni-duesseldorf.sciebo.de/s/oHc608YWQcG45Tf)

```{r, message = FALSE}
# read data ---------------------------------------------------------------
# f <- list.files("danksagungen_tagged_NER/", pattern = "csv", full.names = T)
# d <- do.call(rbind, lapply(1:length(f), function(i) mutate(read_csv(f[i]), doc = i)))

d <- read_csv("danksagungen_tagged_NER.csv")
bawl <- read_xlsx("BAWL-R .xlsx")


```

## Summary statistics

Manual inspection of the data has shown that documents with less than 26 words are artifacts (incomplete documents or statements that the acknowledgments are not included in the online version).

```{r}

d %>% group_by(file) %>% summarise(
  n = n()
) %>% filter(n>26) %>% summarise(
  sum = n(),
  min = min(n),
  max = max(n),
  mean = mean(n),
  median = median(n),
  sd = sd(n)
)



```

Data wrangling

```{r}

# filter all with < 26
exclude_these <- d %>% group_by(file) %>% summarise(
  n = n()
) %>% filter(n<26) %>% select(file) %>% as.vector() %>% unname() %>% unlist()


# exclude
d <- d %>% filter(!file %in% exclude_these)

# check which person names belong together
d$rep <- NA

for(i in 2:nrow(d)) {
  if(!is.na(d$entities[i])) {
    if(d$entities[i] == "PER" &  d$entities[i-1] == "PER" & 
       d$file[i] == d$file[i-1] &
       d$enttype[i] == d$enttype[i-1]) {
      d$rep[i] <- "y"
    }
  }

  # print(i)
}

# number of words per document
n_per_doc <- d %>% group_by(file) %>% summarise(
  n = n()
)


# number of names per document
n_names <- d %>% group_by(file) %>% filter(entities=="PER" & is.na(rep)) %>%
  summarise(
    n_names = n()
  )

# join
n_per_doc <- left_join(n_per_doc, n_names)


# remove unrealistic outliers
# n_per_doc <- filter(n_per_doc, n>20)

# relative frequency of names
n_per_doc$names_rel <- n_per_doc$n_names / n_per_doc$n

```

## Length of each document

```{r}
# plot length
p1 <- ggplot(mutate(n_per_doc, group = 1), aes(x=group, y = n)) +
  geom_beeswarm(col="lightblue") + geom_boxplot(alpha = .5) +
  theme(axis.ticks.x = element_blank(),
        axis.text.x = element_blank()) +
  ylab("Length (in words)") + xlab("") +
  ggtitle("Length") +
  theme(plot.title = element_text(face = "bold", hjust = 0.5))

# plot number of names
p2 <- ggplot(mutate(n_per_doc, group = 1), aes(x=group, y = n_names)) +
  geom_beeswarm(col="deeppink3", alpha = .3) + geom_boxplot(alpha = .5) +
  theme(axis.ticks.x = element_blank(),
        axis.text.x = element_blank()) +
  ylab("# of named entities") + xlab("") +
  ggtitle("# of names") +
  theme(plot.title = element_text(face = "bold", hjust = 0.5))

p1 + p2
# ggsave("length.png", width = 10, height = 4.5)

```

mean and sd:

```{r}

n_per_doc$n %>% mean
n_per_doc$n %>% sd

```


## Parts of speech
```{r}

# plot POS
d$POS <- case_when(d$pos %in% c("ADP", "ADV", "CCONJ", "DET", "NUM",
                       "PART", "PRON", "PUNCT", "SCONJ", 
                       "SPACE", "X") ~"other",
          d$pos %in% c("AUX", "VERB") ~ "verb",
          d$pos == "ADJ" ~ "adjective",
          d$pos == "NOUN" ~ "noun",
          d$pos == "PROPN" ~ "proper name")

d$POS <- factor(d$POS, levels = c("other", "verb", "adjective", "noun", "proper name"))

ggplot(d, aes(x = fct_infreq(factor(file)), 
              fill = POS)) + geom_bar(position = "fill") +
  scale_fill_viridis_d() +
  guides(fill=guide_legend(ncol=1)) +
  xlab("Document") + ylab("n")

```

## Collexeme analysis: early vs. late words

Our qualitative analysis of a subsample has shown that there is a clear divide between early and late words in the acknowledgment sections. As such, we can assume that some words will be more likely to occur in early and other in later parts of an acknowlegdment. 

```{r}

# add absolute and relative position
d$abs_position <- unlist(lapply(1:length(rle(d$file)$lengths), function(i) 1:(rle(d$file)$lengths[i])))

# file length
d_file_lengths <- d %>% group_by(file) %>% summarise(
  length_file = n()
)

# join
d <- left_join(d, d_file_lengths)

# relative position
d$rel_position <- d$abs_position / d$length_file

# se function
se <- function(x) sqrt(var(x) / length(x))

# get and plot mean and absolute relative position
for(i in c(1:3)) {
  assign(paste0("p", i), d %>% filter(POS %in% c("noun", "adjective", "verb")) %>% group_by(lemma, POS) %>% summarise(
  n = n(),
  mean = mean(na.omit(rel_position)),
  sd = sd(na.omit(rel_position)),
  se = se(na.omit(rel_position)),
  min = mean-se,
  max = mean+se
) %>% mutate(LEMMA = toupper(lemma)) %>%
  left_join(., bawl, by = c("LEMMA" = "WORD")) %>%
  filter(n>20) %>%
  mutate("Emotional Valence" = EMO_MEAN) %>%
  filter(POS == c("verb", "adjective", "noun")[i]) %>%
  arrange(mean) %>% 
  ggplot(aes(y = fct_reorder(lemma, mean, .desc = T), x = mean, col = `Emotional Valence`)) +
  geom_point() + 
  geom_errorbar(aes(xmin=min, xmax=max)) +
  facet_wrap(~POS, scales = "free_x") +
  xlab("Mean position") + ylab("Lemma") +
  # guides(col = guide_legend(title = "emotional valence")) +
  # ggtitle("Relative position of word in the text") +
  scale_color_gradient2(limits = c(-3,3), low = "darkblue", mid = "white", high = "darkred")) 
}

p3 + p1 /
  p2 + plot_layout(guides = "collect") +
  plot_annotation("Relative position of word in the text")
# ggsave("position_word.png", width = 13, height = 12)

d %>% filter(POS %in% c("noun", "adjective", "verb")) %>% group_by(lemma, POS) %>% summarise(
  n = n(),
  mean = mean(na.omit(rel_position)),
  sd = sd(na.omit(rel_position)),
  se = se(na.omit(rel_position)),
  min = mean-se,
  max = mean+se
) %>% mutate(LEMMA = toupper(lemma)) %>%
  left_join(., bawl, by = c("LEMMA" = "WORD")) %>%
  filter(n>20) %>%
  filter(POS == c("verb", "adjective", "noun")[1]) %>%
  arrange(mean) %>% 
  ggplot(aes(y = fct_reorder(lemma, mean, .desc = T), x = mean, col = EMO_MEAN)) +
  geom_point() + 
  geom_errorbar(aes(xmin=min, xmax=max)) +
  facet_wrap(~POS, scales = "free") +
  xlab("Mean position") + ylab("Lemma") +
  ggtitle("Relative position of word in the text") +
  scale_color_gradient2(limits = c(-3,3), low = "darkblue", mid = "white", high = "darkred") 
  

# absolute emotional valence and its distribution
emo_tbl <- d %>% filter(POS %in% c("noun", "adjective", "verb")) %>% mutate(LEMMA = toupper(lemma)) %>%
  left_join(., bawl, by = c("LEMMA" = "WORD")) %>% select(LEMMA, POS, EMO_MEAN, rel_position) %>% na.omit %>%
  mutate(emo_abs = abs(EMO_MEAN))

ggplot(emo_tbl, aes(x = rel_position, y = emo_abs)) + geom_smooth()

cor.test(emo_tbl$rel_position, emo_tbl$EMO_MEAN, method = "kendall")


```

Frequency of the word "danken" in each acknowledgment

```{r}

d %>% mutate(dank = grepl("[Dd]ank.*", .$lemma)) %>%
  group_by(file) %>% summarise(
  n_dank = length(which(dank==TRUE)),
  n = n(),
  rel = n_dank / n
) %>% arrange(rel) %>% print(n = 20)

```

## Pattern analysis

The TIGER corpus is used as a baseline to check which n-grams occur with above-chance frequency in the acknowledgments data.

```{r}

# TIGER
tiger <- vroom("../../Corpora/TIGER/tiger_release_aug07.corrected.16012013.conll09",
               delim = "\t", col_names = c("no", "word", "lemma", "a", "POS", "b", "morph", "c","d","e","f","g", "h", "i"))

# add lemma column distinguishing between . and other punctuation marks
tiger$Lemma <- ifelse(tiger$word=="." & tiger$lemma=="--", ".", tiger$lemma)



# sentence by sentence:

# full stops as "breaking points"
fullstop <- which(tiger$Lemma==".")
fullstop[1] <- 1
fullstop[length(fullstop)+1] <- nrow(tiger)


# word form, lemma and POS lists as word vectors
tiger00a <- pblapply(1:(length(fullstop)-1), function(i) paste0(tiger$word[fullstop[i]:fullstop[i+1]]))
tiger01a <- pblapply(1:(length(fullstop)-1), function(i) paste0(tiger$Lemma[fullstop[i]:fullstop[i+1]]))
tiger02a <- pblapply(1:(length(fullstop)-1), function(i) paste0(tiger$POS[fullstop[i]:fullstop[i+1]]))

# find and remove punctuation
find_punctuation <- pblapply(1:length(tiger01a), function(i) grep("^[[:punct:]]+$", tiger00a[[i]]))

for(i in 1:length(tiger00a)) {
  if(length(find_punctuation[[i]]) > 0) {
    tiger00a[[i]] <- tiger00a[[i]][-find_punctuation[[i]]]
    tiger01a[[i]] <- tiger01a[[i]][-find_punctuation[[i]]]
    tiger02a[[i]] <- tiger02a[[i]][-find_punctuation[[i]]]
  }
}


# word form, lemma and POS lists as full sentences
tiger00 <- lapply(1:length(tiger00a), function(i) paste0(tiger00a[[i]], collapse = " "))
tiger01 <- lapply(1:length(tiger01a), function(i) paste0(tiger01a[[i]], collapse = " "))
tiger02 <- lapply(1:length(tiger02a), function(i) paste0(tiger02a[[i]], collapse = " "))

# lemma n-grams
# tigern <- tokens_ngrams(tokens(unlist(tiger01)), n = 2:6, concatenator = " ")
# as.character(tigern) %>% writeLines("tiger_lemma_ngrams.txt")

# pos ngrams
# tigern <- tokens_ngrams(tokens(unlist(tiger02)), n = 2:6, concatenator = " ")
# as.character(tigern) %>% writeLines("tiger_pos_ngrams.txt")

# word form ngrams
# tigern <- tokens_ngrams(tokens(unlist(tiger00)), n = 2:6, concatenator = " ")
# as.character(tigern) %>% writeLines("tiger_word_form_ngrams.txt")


# skipgrams
# tigern2 <- tokens_ngrams(tokens(tiger01), n = 2:6, skip = 1:3, concatenator = " ")


# tiger -------------------------------------------------------------------

tiger <- readLines("tiger_lemma_ngrams.txt")
tiger_tbl <- as_tibble(table(tiger)) %>% arrange(desc(n))
tiger_tbl <- tiger_tbl %>% setNames(c("trigrams", "n_all"))

# ngrams ------------------------------------------------------------------

# add lemma column distinguishing between . and other punctuation marks
d$Lemma <- ifelse(d$tok=="." & d$lemma=="--", ".", d$lemma)

# sentence by sentence:

# full stops as "breaking points"
fullstop <- which(d$Lemma==".")
fullstop[1] <- 1
fullstop[length(fullstop)+1] <- nrow(d)


# word form, lemma and POS lists as word vectors
d00a <- pblapply(1:(length(fullstop)-1), function(i) paste0(d$tok[fullstop[i]:fullstop[i+1]]))
d01a <- pblapply(1:(length(fullstop)-1), function(i) paste0(d$Lemma[fullstop[i]:fullstop[i+1]]))
d02a <- pblapply(1:(length(fullstop)-1), function(i) paste0(d$pos[fullstop[i]:fullstop[i+1]]))

# check that all have the same length
for(i in 1:length(d00a)) {
  if(!(length(d00a[[i]]) == length(d01a[[i]]) &
       length(d00a[[i]]) == length(d02a[[i]]))) {
    print(i)
  }
}

# find and remove punctuation
find_punctuation <- pblapply(1:length(d01a), function(i) grep("^[[:punct:]]+$", d01a[[i]]))

for(i in 1:length(d00a)) {
  if(length(find_punctuation[[i]]) > 0) {
    d00a[[i]] <- d00a[[i]][-find_punctuation[[i]]]
    d01a[[i]] <- d01a[[i]][-find_punctuation[[i]]]
    d02a[[i]] <- d02a[[i]][-find_punctuation[[i]]]
  }
}


# check that all have the same length
for(i in 1:length(d00a)) {
  if(!(length(d00a[[i]]) == length(d01a[[i]]) &
       length(d00a[[i]]) == length(d02a[[i]]))) {
    print(i)
  }
}

# word form, lemma and POS lists as full sentences
d00 <- lapply(1:length(d00a), function(i) paste0(d00a[[i]], collapse = " "))
d01 <- lapply(1:length(d01a), function(i) paste0(d01a[[i]], collapse = " "))
d02 <- lapply(1:length(d02a), function(i) paste0(d02a[[i]], collapse = " "))

# check that all have the same langth
for(i in 1:length(d00)) {
  if(!(wordcount(d00[[i]]) == wordcount(d01[[i]]) &
       wordcount(d00[[i]]) == wordcount(d02[[i]]))) {
    print(i)
  }
}


# remove punctuation everywhere
for(i in 1:length(d00)) {
  d00[[i]] <- gsub("[[:punct:]]", "", d00[[i]])
  d01[[i]] <- gsub("[[:punct:]]", "", d01[[i]])
  d02[[i]] <- gsub("[[:punct:]]", "", d02[[i]])
}


# tokenize

d00_t <- tokens(unlist(d00), remove_punct = T)
d01_t <- tokens(unlist(d01), remove_punct = T)
d02_t <- tokens(unlist(d02), remove_punct = T)

# check if all have the same length
for(i in 1:length(d00_t)) {
  if(!(length(d00_t[[i]]) == length(d01_t[[i]]) &
       length(d00_t[[i]]) == length(d02_t[[i]]))) {
    print(i)
  }
}

# remove the three that do not work for some reason
rmv_these <- c(1427, 1429, 1435)
d00_t <- d00_t[-rmv_these]
d01_t <- d01_t[-rmv_these]
d02_t <- d02_t[-rmv_these]

# ngrams:

# lemma ngrams
d3 <- tokens_ngrams(d01_t, n = 2:6, concatenator = " ")
d3 <- as.character(d3)

# lowercase:
d3 <- tolower(d3)

# word form ngrams
d3_wf <- tokens_ngrams(d01_t, n = 2:6, concatenator = " ")
d3_wf <- as.character(d3_wf)

# pos ngrams
d3_pos <- tokens_ngrams(d02_t, n = 2:6, concatenator = " ")
d3_pos <- as.character(d3_pos)


# lemma n-gram table
d_tbl <- as_tibble(table(d3)) %>% setNames(c("trigrams", "n"))
d_tbl <- d_tbl %>% arrange(desc(n))

# join tables

# make tiger ngrams lowercase
tiger_tbl$trigrams <- tolower(tiger_tbl$trigrams)
tiger_tbl <- tiger_tbl %>% group_by(trigrams) %>% summarise(
  n_all = sum(n_all)
) %>% arrange(desc(n_all))

d_tbl <- left_join(d_tbl, tiger_tbl)
d_tbl <- d_tbl %>% replace_na(list(n = 0, n_all = 0))

# convert all to lowercase
# d_tbl_backup <- d_tbl
# d_tbl$trigrams <- tolower(d_tbl$trigrams)
# d_tbl <- d_tbl %>% group_by(trigrams) %>% summarise(
#   n = sum(n),
#   n_all = sum(n_all)
# )

# get collexemes
d_collex <- d_tbl %>% as.data.frame %>% collex.dist()

# results without punctuation
d_collex[grep("[[:punct:]]", d_collex$COLLEX, invert = T),] # %>% writexl::write_xlsx("dank_collex.xlsx")

# add wordcount
d_collex$wordcount <- sapply(1:nrow(d_collex), function(i) wordcount(d_collex$COLLEX[i]))

# without punctuation & 3+ words
d_collex[grep("[[:punct:]]", d_collex$COLLEX, invert = T),] %>%
  filter(wordcount>3) # %>% writexl::write_xlsx("dank_collex.xlsx")


# similarity --------------------------------------------------------------

# limit to the most frequent n-grams
# --> to find them, first create a dataframe of
# word, lemma, pos ngrams

df <- tibble(word = d3_wf, lemma = d3, pos = d3_pos)
df <- df %>% group_by(lemma) %>% add_tally()
df1 <- filter(df, n >= 10) # only keep n-grams attested
                                        # 10 or more times

# add column with lowercase lemma
df1$Lemma <- df1$lemma
df1$lemma <- tolower(df1$lemma)

# create list with individual words/lemmas/pos
# for each ngram
df1 %>% arrange(desc(n))

df2 <- df1 %>% group_by(word, pos, lemma) %>% summarise(
  n = sum(unique(n))
) %>% arrange(desc(n))

# df2 <- df1 %>% arrange(desc(lemma))
df2 <- df2[-which(duplicated(df2$lemma)),]

# huge matrix with unique lemmas, word forms, and POS tags as
# colnames and n-grams as rownames

# rwnms <- c(levels(factor(unlist(strsplit(df2$word, " ")))), 
#   levels(factor(unlist(strsplit(df2$lemma, " ")))),
#   levels(factor(unlist(strsplit(df2$pos, " ")))))

# update: only lemmas yields better results (for obvious reasons,
# as here we are only interested in similarities pertaining to
# the involved lemmas, not su much syntactic patterns etc.)

# row names for the matrix
rwnms <- levels(factor(unlist(strsplit(df2$lemma, " "))))





# create empty matrix
m <- matrix(ncol = length(rwnms), nrow = nrow(df2))



# fill matrix
for(i in 1:nrow(m)) {
  m[i,] <- as.numeric(rwnms %in% unlist(strsplit(df2$lemma[i], " ")))
  # m[i,] <- as.numeric(rwnms %in% c(unlist(strsplit(df2$lemma[i], " ")),
  #                                  unlist(strsplit(df2$word[i], " ")),
  #                                  unlist(strsplit(df2$pos[i], " "))))
}


# add colnames and rownames
colnames(m) <- rwnms
rownames(m) <- df2$lemma




# get Euclidean distance between n-grams
m_dist <- dist(m)

# square Euclidean distance
m_dist2 <- m_dist^2
m_dist_matrix <- as.matrix(m_dist2)


# get tibble that allows for sorting
# the n-grams according to their
# similarity: similarity score in
# one column, n-gram 1 in another,
# n-gram2 in the third

m_dist_df <- as.data.frame(m_dist_matrix) %>% 
  rownames_to_column() %>% 
  as_tibble()
m_dist_df <- m_dist_df %>% pivot_longer(cols = 2:length(m_dist_df))
colnames(m_dist_df) <- c("ngram1", "ngram2", "dist")
m_dist_df1 <- m_dist_df %>% 
  filter(dist > 0) %>% 
  arrange(dist)

# add frequency of each n-gram
ngram_freqs <- select(ungroup(df2), lemma, n)

# m_dist_df als data table
m_dist_df1a <- as.data.table(m_dist_df1)
ngram_freqs1 <- as.data.table(ngram_freqs)

m_distdf1b <- merge(m_dist_df1a, ngram_freqs1, by.x = "ngram1",
                  by.y = "lemma")

m_distdf1c <- merge(m_distdf1b, ngram_freqs1, by.x = "ngram2",
                    by.y = "lemma")


# add wordcount
m_distdf1c[, wordcountx := pbsapply(1:nrow(m_distdf1c), function(i) wordcount(m_distdf1c$ngram1[i]))]
m_distdf1c[, wordcounty := pbsapply(1:nrow(m_distdf1c), function(i) wordcount(m_distdf1c$ngram2[i]))]

# add "normalized" frequency by dividing by wordcount
m_distdf1c[, norm_freq1 := n.x / wordcountx]
m_distdf1c[, norm_freq2 := n.y / wordcounty]



# if dist <= 2, only keep the item
# with the higher normalized frequency

m_distdf1c[dist <= 2 & norm_freq1 < norm_freq2, rmv := "x"]
m_distdf1c[dist <= 2 & norm_freq1 > norm_freq2, rmv := "y"]


# list of items to be removed
rmv <- unique(c(m_distdf1c[rmv=="x"]$ngram2, m_distdf1c[rmv=="y"]$ngram1))

# ngram list with items to be omitted
df1a <- df1[-which(df1$lemma %in% rmv),]

# same for collexeme table
d_collex1 <- d_collex %>% filter(!COLLEX %in% rmv & O.CXN1 > 0)
d_collex1a <- d_collex1[grep("(?<= )[[:punct:]]", d_collex1$COLLEX, invert = T, perl = T),] %>%
  filter(SIGNIF!="ns")
d_collex1a$LOGFREQ <- log(d_collex1a$O.CXN1)
d_collex1aa <- filter(d_collex1a, ASSOC != "n_all")

# omit all items containing numbers or NA
d_collex1a <- d_collex1a[!grepl("[0-9]|na ", d_collex1a$COLLEX),]
d_collex1aa <- d_collex1aa[!grepl("[0-9]|na ", d_collex1aa$COLLEX),]

# table
d_collex1aa %>% datatable(escape = FALSE, filter = list(position = "top"))

# make wordcloud
set.seed(1985)
wordcloud2(select(d_collex1a, COLLEX, O.CXN1), fontFamily = "Arial",
           fontWeight = "normal", 
           minRotation = 0, maxRotation = 0)


# only with attracted collexemes
# png("wordcloud01_col.png", width = 6, height = 6, un = "in", res = 400)
set.seed(1985)
wordcloud(words = filter(d_collex1aa, O.CXN1 < 1000)$COLLEX,
          freq = filter(d_collex1aa, O.CXN1 < 1000)$O.CXN1,
          colors = terrain.colors(7),
          scale = c(2,.2), min.freq = 15)
# dev.off()

# wordcloud based on collostruction strength
 png("wordcloud_collex_color.png", width = 6, height = 6, un = "in", res = 900)
# svg("wordcloud_collex.svg", width = 3, height = 3) - not working, use export function in RStudio
set.seed(1985)
wordcloud(words = d_collex1aa$COLLEX,
          freq = d_collex1aa$COLL.STR.LOGL,
          colors = terrain.colors(7),
          scale = c(1.5,.05), min.freq = 7)
 dev.off()






```



## Qualitative analysis

```{r}

d <- read_xlsx("Qualitative_Analyse/CodierteSegmente.xlsx")

# add index number
d$no <- 1:nrow(d)

# identify duplicates
d <- left_join(d,tibble(Segment = unique(d$Segment),
                    No = 1:length(unique(d$Segment))))

duplicate_numbers <- d[which(duplicated(d$No)),]$no

# read tagged data --------------------------------------------------------
d1 <- read_csv("Qualitative_Analyse/codierte_segmente_tagged.csv")

# add index number to join dataframes
d1$no <- as.numeric(gsub("[^0-9]", "", d1$file))-1


# get codes ---------------------------------------------------------------

d <- separate_wider_delim(d, cols = Code, delim = ">", 
                     names_sep = "_", too_few = "align_start")

# join dataframes
d1 <- left_join(d1, 
          select(d, c("no", starts_with("Code"))))


# distinctive collexeme analysis:
# privat (private) vs. beruflich (professional)

filter(d1, pos %in% c("NOUN", "ADJ", "VERB") & !no %in% duplicate_numbers) %>% 
  select(Code_2, lemma) %>%
  as.data.frame() %>%
  collex.dist(raw = T, reverse = F)#%>% writexl::write_xlsx("collex_danksagungen_beruflich_privat.xlsx")

# attracted to "beruflich"
filter(d1, pos %in% c("NOUN", "ADJ", "VERB") & !no %in% duplicate_numbers) %>% 
  select(Code_2, lemma) %>%
  as.data.frame() %>%
  collex.dist(raw = T, reverse = F) %>% 
  filter(O.CXN1 >2 &  ASSOC==" Beruflich ") %>%
  select(COLLEX, O.CXN1, COLL.STR.LOGL, SHARED) %>% datatable() #%>%
   #writexl::write_xlsx("collex_beruflich.xlsx")

# attracted to "privat"
filter(d1, pos %in% c("NOUN", "ADJ", "VERB") & !no %in% duplicate_numbers) %>% 
  select(Code_2, lemma) %>%
  as.data.frame() %>%
  collex.dist(raw = T, reverse = T) %>% 
  filter(O.CXN2 >2 & ASSOC==" Privat ") %>%
  select(COLLEX, O.CXN2, COLL.STR.LOGL, SHARED) %>% datatable() #%>%
 # writexl::write_xlsx("collex_privat.xlsx")

```


Position in text

```{r}

# raw texts
f <- list.files("danksagungen_sample/", full.names = TRUE)
d2 <- do.call(rbind, lapply(1:length(f), function(i) mutate(tibble(text = read_lines(f[i])), file = gsub(".*/", "", f[i]))))
d2$Dokumentname <- gsub("\\.txt", "", d2$file)
d2$Dokumentname <- as.numeric(d2$Dokumentname)

# add full texts to segments
d <- left_join(d, select(d2, Dokumentname, text))

# start and end position
d$start <- sapply(1:nrow(d), function(i) unlist(str_locate_all(d$text[i], fixed(d$Segment[i])))[1])
d$end <- sapply(1:nrow(d), function(i) unlist(str_locate_all(d$text[i], fixed(d$Segment[i])))[2])

# number of characters
d$nchar <- sapply(1:nrow(d), function(i) nchar(d$text[i]))

# normalized start and end position
d$start_norm <- d$start / d$nchar
d$end_norm   <- d$end / d$nchar

# plot

d$Domain <- ifelse(grepl("Beruflich", d$Code_2), "professional", "private")

(p1 <- ggplot(filter(d, !no %in% duplicate_numbers), aes(x = Domain, y = start_norm, fill = Domain)) +
  geom_beeswarm(col="blue", size = .5) +
  geom_violin(alpha = .2) + 
  guides(fill = guide_legend(title = "Domain")) +
  xlab("Domain") + ylab("Start of segment (normalized)") +
  guides(fill = "none") + scale_fill_manual(values = c("orange", "blue")) + coord_flip())
#  ggsave("beruflich_privat.png")

```

Visualization with tiles

```{r}

# get positions
for(j in 1:length(levels(factor(d$Dokumentname)))) {
  # current document
  d_cur <- filter(d, Dokumentname==levels(factor(d$Dokumentname))[j])
  
  # current vector - default color: grey
  cur <- rep("grey", 100)
  
  # change color for the coded segments
  cur_list <- lapply(1:length(round(d_cur$start_norm*100)),
                     function(i) round(d_cur$start_norm*100)[i]:round(d_cur$end_norm*100)[i])
  
  for(i in 1:length(cur_list)) {
    if(d_cur$Code_2[i]==" Privat ") {
      cur[cur_list[[i]]] <- "orange"
    } else {
      cur[cur_list[[i]]] <- "blue"
    }
    
    # print(i)
    
  }
  
  # as table with position and color
  cur_tbl <- tibble(position = 1:100, col = cur, doc = j)
  
  # combine with others
  if(j == 1) {
    all_tbl <- cur_tbl
  } else {
    all_tbl <- rbind(all_tbl, cur_tbl)
  }
  
}



# helper function from https://dominicroye.github.io/en/2018/how-to-create-warming-stripes-in-r/
theme_strip <- theme_minimal()+
  theme(axis.text.y = element_blank(),
        axis.line.y = element_blank(),
        axis.title = element_blank(),
        panel.grid.major = element_blank(),
        # legend.title = element_blank(),
        axis.text.x = element_text(vjust = 3),
        panel.grid.minor = element_blank(),
        plot.title = element_text(size = 14, face = "bold")
  )


# visualize
all_tbl$col <- factor(all_tbl$col, levels = c("blue", "orange", "grey"))
all_tbl

(p2 <- ggplot(all_tbl, aes(x = position, y = 1, fill = col)) +
  geom_tile() +
    theme(axis.text.y = element_blank(),
        axis.line.y = element_blank(),
        axis.line.x = element_blank(),
        #axis.title = element_blank(),
        panel.grid.major = element_blank(),
        # legend.title = element_blank(),
        #axis.text.x = element_text(vjust = 3),
        panel.grid.minor = element_blank(),
        plot.title = element_text(size = 14, face = "bold")
  ) +
  facet_wrap(doc ~ .,ncol=1, strip.position  = "left") +
  scale_fill_identity(guide = 'legend',
                      labels = c("professional", "private", "not coded")) +
  guides(fill = guide_legend(title = "Domain")) +
  theme(strip.text.y.left = element_text(angle = 0)) +
  #theme(axis.text.x = element_blank()) + 
    xlab("Position") + ylab("Document") +
    scale_x_continuous(breaks = NULL))
# ggsave("beruflich_privat_tiles.png", width = 6.5, height = 5, bg="white")

# p2 + p1
# ggsave("domains.png", width = 13, height = 6)

```


